Wikipedia Text Mining and Entropy Analysis

### 2018-12-06 wiki_entropy/wiki_entropy.Rmd
typo fix in relative slope

    df %>%
      inner_join(selected_pos, by = c("length", "word_order")) %>% 
      group_by(length, word_order) %>%
      summarise(entropy = entropy(n, unit = "log2")) %>%
      lm(entropy ~ length + I(length^2) ++ word_order, data  = .) %>%
      tidy() %>%
      filter(term == "word_order")
  }

>>>>

    df %>%
      inner_join(selected_pos, by = c("length", "word_order")) %>% 
      group_by(length, word_order) %>%
      summarise(entropy = entropy(n, unit = "log2")) %>%
      lm(entropy ~ length + I(length^2) + word_order, data  = .) %>%
      tidy() %>%
      filter(term == "word_order")
  }
